\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2020-02-06 submission/manuscript.Rmd
Geographic coordinates setup.

\newpage
## Materials and Methods
### Sampling
Leaves of *Cymodocea nodosa* were sampled in a *Cymodocea nodosa* meadow in the Bay of Saline (45°7´5˝N, 13°37´20˝E) and in a *Cymodocea nodosa* meadow invaded by *Caulerpa cylindracea* in the proximity of the village of Funtana (45°10´39˝N, 13°35´42˝E). Thalli of *Caulerpa cylindracea* were sampled in the same *Cymodocea nodosa* invaded meadow in Funtana and on a locality of only *Caulerpa cylindracea* located in the proximity of the invaded meadow. Leaves and thalli were collected on the same day in two contrasting seasons, on 4 December 2017 and 18 June 2018. During spring 2018 the *Cymodocea nodosa* meadow in the Bay of Saline decayed to an extent that no leaves could be retrieved (Najdek *et al.*, unpublished data). Leaves and thalli were collected by diving and transported to the laboratory in containers placed on ice and filled with site seawater. Upon arrival to the laboratory, *Cymodocea nodosa* leaves were cut into sections of 1 -- 2 \si{\cm}, while *Caulerpa cylindracea* thalli were cut into 5 -- 8 \si{\cm} long sections. Leaves and thalli were washed three times with sterile artificial seawater (ASW) to remove loosely attached microbial cells.

### DNA Isolation
The DNA was isolated according to the protocol for isolation from filters described in @Massana1997. This protocol was modified and adapted for DNA isolation from microbial communities from macrophyte surfaces as described below. 5 \si{\ml} of lysis buffer (40 \si{\milli\Molar} EDTA, 50 \si{\milli\Molar} Tris-HCl, 0.75 \si{\Molar} sucrose; pH 8.3) was added to 1 \si{\g} wet weight of leaves or \si{\g} wet-weight of thalli. Lysozyme was added (final concentration 1 \si{\mg\per\ml}) and the mixture was incubated at 37 \si{\degreeCelsius} for 30 \si{\minute}. Subsequently, proteinase K (final concentration 0.5 \si{\mg\per\ml}) and SDS (final concentration 1 \si{\percent}) were added and the samples were incubated at 55 \si{\degreeCelsius} for 2 \si{\hour}. Following the incubation, tubes were vortexed for 10 \si{\minute} and the mixture containing lyzed epiphytic cells was separated from host leaves or thalli by transferring the solution into a clean tube. The lysate was extracted twice with a mixture of phenol:chloroform:isoamyl alcohol (25:24:1; pH 8) and once with chloroform:isoamyl alcohol (24:1). After each organic solvent mixture addition tubes were slightly vortexed and centrifuged at 4,500 × g for 10 \si{\minute}. Following each centrifugation aqueous phases were retrieved. After the final extraction 1/10 of chilled 3 \si{\Molar} sodium acetate (pH 5.2) was added. DNA was precipitated by adding 1 volume of chilled isopropanol, incubating the mixtures overnight at \num{-20} °C and centrifuging at 16,000 × g and 4 \si{\degreeCelsius} for 20 \si{\minute}. The pellet was washed twice with 1 \si{\ml} of chilled isopropanol and centrifuged after each washing step at 20,000 × g and 4 \si{\degreeCelsius} for 10 \si{\minute}. After the first washing step duplicate pellets form the same sample were pooled and transferred to a clean 1.5 \si{\ml} tube. The dried pellet was resuspended in 100 \si{\ul} of deionized water.

>>>>

\newpage
## Materials and Methods
### Sampling
Leaves of *Cymodocea nodosa* were sampled in a *Cymodocea nodosa* meadow in the Bay of Saline (\ang{45;7;5} N, \ang{13;37;20} E) and in a *Cymodocea nodosa* meadow invaded by *Caulerpa cylindracea* in the proximity of the village of Funtana (\ang{45;10;39} N, \ang{13;35;42} E). Thalli of *Caulerpa cylindracea* were sampled in the same *Cymodocea nodosa* invaded meadow in Funtana and on a locality of only *Caulerpa cylindracea* located in the proximity of the invaded meadow. Leaves and thalli were collected on the same day in two contrasting seasons, on 4 December 2017 and 18 June 2018. During spring 2018 the *Cymodocea nodosa* meadow in the Bay of Saline decayed to an extent that no leaves could be retrieved (Najdek *et al.*, unpublished data). Leaves and thalli were collected by diving and transported to the laboratory in containers placed on ice and filled with site seawater. Upon arrival to the laboratory, *Cymodocea nodosa* leaves were cut into sections of 1 -- 2 \si{\cm}, while *Caulerpa cylindracea* thalli were cut into 5 -- 8 \si{\cm} long sections. Leaves and thalli were washed three times with sterile artificial seawater (ASW) to remove loosely attached microbial cells.

### DNA Isolation
The DNA was isolated according to the protocol for isolation from filters described in @Massana1997. This protocol was modified and adapted for DNA isolation from microbial communities from macrophyte surfaces as described below. 5 \si{\ml} of lysis buffer (40 \si{\milli\Molar} EDTA, 50 \si{\milli\Molar} Tris-HCl, 0.75 \si{\Molar} sucrose; pH 8.3) was added to 1 \si{\g} wet weight of leaves or \si{\g} wet-weight of thalli. Lysozyme was added (final concentration 1 \si{\mg\per\ml}) and the mixture was incubated at 37 \si{\degreeCelsius} for 30 \si{\minute}. Subsequently, proteinase K (final concentration 0.5 \si{\mg\per\ml}) and SDS (final concentration 1 \si{\percent}) were added and the samples were incubated at 55 \si{\degreeCelsius} for 2 \si{\hour}. Following the incubation, tubes were vortexed for 10 \si{\minute} and the mixture containing lyzed epiphytic cells was separated from host leaves or thalli by transferring the solution into a clean tube. The lysate was extracted twice with a mixture of phenol:chloroform:isoamyl alcohol (25:24:1; pH 8) and once with chloroform:isoamyl alcohol (24:1). After each organic solvent mixture addition tubes were slightly vortexed and centrifuged at 4,500 × g for 10 \si{\minute}. Following each centrifugation aqueous phases were retrieved. After the final extraction 1/10 of chilled 3 \si{\Molar} sodium acetate (pH 5.2) was added. DNA was precipitated by adding 1 volume of chilled isopropanol, incubating the mixtures overnight at \num{-20} °C and centrifuging at 16,000 × g and 4 \si{\degreeCelsius} for 20 \si{\minute}. The pellet was washed twice with 1 \si{\ml} of chilled 70 \si{\percent} ethanol and centrifuged after each washing step at 20,000 × g and 4 \si{\degreeCelsius} for 10 \si{\minute}. After the first washing step duplicate pellets form the same sample were pooled and transferred to a clean 1.5 \si{\ml} tube. The dried pellet was resuspended in 100 \si{\ul} of deionized water.

### 2020-02-06 submission/manuscript.tex
Geographic coordinates setup.

Leaves of \emph{Cymodocea nodosa} were sampled in a \emph{Cymodocea
nodosa} meadow in the Bay of Saline (45°7´5˝N, 13°37´20˝E) and in a
\emph{Cymodocea nodosa} meadow invaded by \emph{Caulerpa cylindracea} in
the proximity of the village of Funtana (45°10´39˝N, 13°35´42˝E). Thalli
of \emph{Caulerpa cylindracea} were sampled in the same \emph{Cymodocea
nodosa} invaded meadow in Funtana and on a locality of only
\emph{Caulerpa cylindracea} located in the proximity of the invaded
meadow. Leaves and thalli were collected on the same day in two
contrasting seasons, on 4 December 2017 and 18 June 2018. During spring
2018 the \emph{Cymodocea nodosa} meadow in the Bay of Saline decayed to
an extent that no leaves could be retrieved (Najdek \emph{et al.},
unpublished data). Leaves and thalli were collected by diving and
transported to the laboratory in containers placed on ice and filled
with site seawater. Upon arrival to the laboratory, \emph{Cymodocea
nodosa} leaves were cut into sections of 1 -- 2 \si{\cm}, while
\emph{Caulerpa cylindracea} thalli were cut into 5 -- 8 \si{\cm} long
sections. Leaves and thalli were washed three times with sterile
artificial seawater (ASW) to remove loosely attached microbial cells.

@@

The DNA was isolated according to the protocol for isolation from
filters described in Massana \emph{et al.} (1997). This protocol was
modified and adapted for DNA isolation from microbial communities from
macrophyte surfaces as described below. 5 \si{\ml} of lysis buffer (40
\si{\milli\Molar} EDTA, 50 \si{\milli\Molar} Tris-HCl, 0.75 \si{\Molar}
sucrose; pH 8.3) was added to 1 \si{\g} wet weight of leaves or \si{\g}
wet-weight of thalli. Lysozyme was added (final concentration 1
\si{\mg\per\ml}) and the mixture was incubated at 37 \si{\degreeCelsius}
for 30 \si{\minute}. Subsequently, proteinase K (final concentration 0.5
\si{\mg\per\ml}) and SDS (final concentration 1 \si{\percent}) were
added and the samples were incubated at 55 \si{\degreeCelsius} for 2
\si{\hour}. Following the incubation, tubes were vortexed for 10
\si{\minute} and the mixture containing lyzed epiphytic cells was
separated from host leaves or thalli by transferring the solution into a
clean tube. The lysate was extracted twice with a mixture of
phenol:chloroform:isoamyl alcohol (25:24:1; pH 8) and once with
chloroform:isoamyl alcohol (24:1). After each organic solvent mixture
addition tubes were slightly vortexed and centrifuged at 4,500 × g for
10 \si{\minute}. Following each centrifugation aqueous phases were
retrieved. After the final extraction 1/10 of chilled 3 \si{\Molar}
sodium acetate (pH 5.2) was added. DNA was precipitated by adding 1
volume of chilled isopropanol, incubating the mixtures overnight at
\num{-20} °C and centrifuging at 16,000 × g and 4 \si{\degreeCelsius}
for 20 \si{\minute}. The pellet was washed twice with 1 \si{\ml} of
chilled isopropanol and centrifuged after each washing step at 20,000 ×
g and 4 \si{\degreeCelsius} for 10 \si{\minute}. After the first washing
step duplicate pellets form the same sample were pooled and transferred
to a clean 1.5 \si{\ml} tube. The dried pellet was resuspended in 100
\si{\ul} of deionized water.

>>>>

Leaves of \emph{Cymodocea nodosa} were sampled in a \emph{Cymodocea
nodosa} meadow in the Bay of Saline (\ang{45;7;5} N, \ang{13;37;20} E)
and in a \emph{Cymodocea nodosa} meadow invaded by \emph{Caulerpa
cylindracea} in the proximity of the village of Funtana (\ang{45;10;39}
N, \ang{13;35;42} E). Thalli of \emph{Caulerpa cylindracea} were sampled
in the same \emph{Cymodocea nodosa} invaded meadow in Funtana and on a
locality of only \emph{Caulerpa cylindracea} located in the proximity of
the invaded meadow. Leaves and thalli were collected on the same day in
two contrasting seasons, on 4 December 2017 and 18 June 2018. During
spring 2018 the \emph{Cymodocea nodosa} meadow in the Bay of Saline
decayed to an extent that no leaves could be retrieved (Najdek \emph{et
al.}, unpublished data). Leaves and thalli were collected by diving and
transported to the laboratory in containers placed on ice and filled
with site seawater. Upon arrival to the laboratory, \emph{Cymodocea
nodosa} leaves were cut into sections of 1 -- 2 \si{\cm}, while
\emph{Caulerpa cylindracea} thalli were cut into 5 -- 8 \si{\cm} long
sections. Leaves and thalli were washed three times with sterile
artificial seawater (ASW) to remove loosely attached microbial cells.

@@

The DNA was isolated according to the protocol for isolation from
filters described in Massana \emph{et al.} (1997). This protocol was
modified and adapted for DNA isolation from microbial communities from
macrophyte surfaces as described below. 5 \si{\ml} of lysis buffer (40
\si{\milli\Molar} EDTA, 50 \si{\milli\Molar} Tris-HCl, 0.75 \si{\Molar}
sucrose; pH 8.3) was added to 1 \si{\g} wet weight of leaves or \si{\g}
wet-weight of thalli. Lysozyme was added (final concentration 1
\si{\mg\per\ml}) and the mixture was incubated at 37 \si{\degreeCelsius}
for 30 \si{\minute}. Subsequently, proteinase K (final concentration 0.5
\si{\mg\per\ml}) and SDS (final concentration 1 \si{\percent}) were
added and the samples were incubated at 55 \si{\degreeCelsius} for 2
\si{\hour}. Following the incubation, tubes were vortexed for 10
\si{\minute} and the mixture containing lyzed epiphytic cells was
separated from host leaves or thalli by transferring the solution into a
clean tube. The lysate was extracted twice with a mixture of
phenol:chloroform:isoamyl alcohol (25:24:1; pH 8) and once with
chloroform:isoamyl alcohol (24:1). After each organic solvent mixture
addition tubes were slightly vortexed and centrifuged at 4,500 × g for
10 \si{\minute}. Following each centrifugation aqueous phases were
retrieved. After the final extraction 1/10 of chilled 3 \si{\Molar}
sodium acetate (pH 5.2) was added. DNA was precipitated by adding 1
volume of chilled isopropanol, incubating the mixtures overnight at
\num{-20} °C and centrifuging at 16,000 × g and 4 \si{\degreeCelsius}
for 20 \si{\minute}. The pellet was washed twice with 1 \si{\ml} of
chilled 70 \si{\percent} ethanol and centrifuged after each washing step
at 20,000 × g and 4 \si{\degreeCelsius} for 10 \si{\minute}. After the
first washing step duplicate pellets form the same sample were pooled
and transferred to a clean 1.5 \si{\ml} tube. The dried pellet was
resuspended in 100 \si{\ul} of deionized water.
